Mahotas: Open source software for scriptable computer vision

### 2012-11-21 paper.tex
BLD Use pdflatex (which arXiv uses)

\documentclass{scrartcl}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{tikz}
\usepackage{python}
\usepackage{fontspec}
\usepackage[%
    natbib=true,%
    useprefix=true,
    backend=biber,%
    backref=true,%
    citestyle=authoryear-comp,%
    bibstyle=authoryear,%
    maxbibnames=24,%
    maxcitenames=2,%
]{biblatex}

\hypersetup{%
    bookmarks=true,
    colorlinks=true,
    pdftitle={Mahotas: Open source software for scriptable computer vision},
    pdfauthor={Luis Pedro Coelho},
    citecolor=pondgreen,
    urlcolor=toastedchilipowder,
    linkcolor=toastedchilipowder,
}
\font\CodeFont="DejaVu Sans Mono" at 8pt
\setmainfont[Mapping=tex-text]{Linux Libertine O}
\newcommand*{\cpp}{{C\nolinebreak[4]\hspace{-.05em}\raisebox{.4ex}{\tiny\textbf{++}}}}
\def\code#1{\bgroup\CodeFont #1\egroup}
\addbibresource{references.bib}

@@

This functions retrieves the arguments, performs some sanity checks, performs a
bit of initialisation, and finally, switches in the input type with the help of
the \code{SAFE\_SWITCH\_ON\_INTEGER\_TYPES()} macro, which call the right
specialisation of the template that does the actual work. In this example
\code{erode} implements erosion:

@@

Python is an ideal language for fast development of both applications and
scientific software. For this platform, Mahotas is a fast library of computer
vision and image processing functions. It is implemented in \cpp{}, as the
standard Python interpreter is too slow for a direct Python implementation.
However, all of the Python interface code is hand-written, as opposed to using
automatic interface generators like Swig~\cite{Beazley2003599}. This is more
work, but the end result is of much higher quality, especially when it comes to
giving useful error messages (e.g., when a type mismatch occurs, an automatic
system will often be forced to resort to a generic message as it does not have
any knowledge of what the arguments mean besides their automatically inferred
types).

@@

\printbibliography
\end{document}

>>>>

\documentclass{scrartcl}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{tikz}
\usepackage{python}
\usepackage{libertine}
\usepackage{DejaVuSansMono}
\usepackage{natbib}
\hypersetup{%
    bookmarks=true,
    colorlinks=true,
    pdftitle={Mahotas: Open source software for scriptable computer vision},
    pdfauthor={Luis Pedro Coelho},
    citecolor=pondgreen,
    urlcolor=toastedchilipowder,
    linkcolor=toastedchilipowder,
}

\newcommand*{\cpp}{{C\nolinebreak[4]\hspace{-.05em}\raisebox{.4ex}{\tiny\textbf{++}}}}
\let\code\texttt
\bibliographystyle{natbib}

@@

This functions retrieves the arguments, performs some sanity checks, performs a
bit of initialisation, and finally, switches in the input type with the help of
the \code{SAFE\_\-SWITCH\_\-ON\_\-INTEGER\_\-TYPES()} macro, which call the right
specialisation of the template that does the actual work. In this example
\code{erode} implements erosion:

@@

Python is an ideal language for fast development of both applications and
scientific software. For this platform, Mahotas is a fast library of computer
vision and image processing functions. It is implemented in \cpp{}, as the
standard Python interpreter is too slow for a direct Python implementation.
However, all of the Python interface code is hand-written, as opposed to using
automatic interface generators like Swig~\citep{Beazley2003599}. This is more
work, but the end result is of much higher quality, especially when it comes to
giving useful error messages (e.g., when a type mismatch occurs, an automatic
system will often be forced to resort to a generic message as it does not have
any knowledge of what the arguments mean besides their automatically inferred
types).

@@

\bibliography{references}
\end{document}
